HPC--101\\Onboarding

### 2016-02-22 hpc_101/paper.tex
changes to srun example and sbatch examples

\subsection{Interactive Job -- srun}
\frametitle{SLURM Job Scripts}
\begin{frame}
\frametitle{Interactive Job with SLURM}
	\begin{block}{Interactive session (no X11)}\tiny
	$[$login \ctilde$]$\$ srun \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 5 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00:00 \ddash{}pty /bin/bash
	\end{block}

	\begin{block}{Interactive session (with X11)}\tiny
		\begin{enumerate}
			\item Connect via SSH using the -Y option, X11 forwarding enabled
			\item run srun.x11 to start a session on a node
		\end{enumerate}
		~\\
		~\\
		$[$local \ctilde$]$\$ ssh -Y user99@uhhpc1.its.hawaii.edu	~\\
		$[$login \ctilde$]$\$ srun.x11 \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 5 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00:00	~\\
		$[$compute-0001 \ctilde$]$\$ xterm	~\\
	\end{block}
\end{frame}

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=MPI\_example
\#SBATCH \ddash{}partition=exclusive.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=4
\#SBATCH \ddash{}tasks-per-node=20
\#SBATCH \ddash{}cpus-per-task=1
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                             
\#SBATCH \ddash{}error=hello-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=hello-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                              
\#SBATCH \ddash{}error=hello-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=hello-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

>>>>

\subsection{Interactive Job -- srun}
\frametitle{SLURM Job Scripts}
\begin{frame}
\frametitle{Interactive Job with SLURM}
	\begin{block}{Interactive session (no X11)}\tiny
	$[$login \ctilde$]$\$ srun \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 1 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00:00 \ddash{}pty /bin/bash
          ~\\
          ~\\
          \hrule
          ~\\
	$[$login \ctilde$]$\$ srun -I -p sb.q -N 1 -c 1 -n 1 -t 0-01:00:00 \ddash{}pty /bin/bash

	\end{block}

	\begin{block}{Interactive session (with X11)}\tiny
		\begin{enumerate}
			\item Connect via SSH using the -Y option, X11 forwarding enabled
			\item run srun.x11 to start a session on a node
		\end{enumerate}
		~\\
		~\\
		$[$local \ctilde$]$\$ ssh -Y user99@uhhpc1.its.hawaii.edu	~\\
		$[$login \ctilde$]$\$ srun.x11 \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 1 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00:00	~\\
		$[$compute-0001 \ctilde$]$\$ xterm	~\\
	\end{block}
\end{frame}

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=MPI\_example
\#SBATCH \ddash{}partition=exclusive.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=4
\#SBATCH \ddash{}tasks-per-node=20
\#SBATCH \ddash{}cpus-per-task=1
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                             
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid.
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid.
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                              
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid.
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid.
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org
